\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-06 paper/paper.tex
Architecture first draft

In this paper, we present Dark Decoys, a deployable Refraction Networking scheme that
overcomes these issues. Dark Decoys leverages the (primarily) unused address
space that is reachable through the deploying ISP. Rather than rely on existing
sites as reachable decoy sites that must be involved in each proxy connection,
Dark Decoys create seemingly legitimate hosts at new IP addresses. These
invented hosts are indistinguishable from normal hosts to the censor, but can
be used by clients as one-time proxies.

@@

\section{Architecture}
% 3 pages
-Registration
-Dark decoy selection (seed -> IP)
-Connection to Dark Decoy Application (DD App)
-IPv6 vs IPv4 dark decoys

@@

Application choices:
-obfs4  (could we test this?)
-Masked sites (implemented)
-TLS 1.3 eSNI

-Takeover of masked site TLS connection (client/server random from masked site, master secret from registration)

-Masked site slection: How do we get the list of masked sites? Alexa list? passive observation?

>>>>

In this paper, we present Dark Decoys, a deployable Refraction Networking scheme that
overcomes the limits on decoys and performance. Dark Decoys leverages the (primarily) unused address
space that is reachable through the deploying ISP. Rather than rely on existing
sites as reachable decoy sites that must be involved in each proxy connection,
Dark Decoys create seemingly legitimate hosts at new IP addresses. These
invented hosts are indistinguishable from normal hosts to the censor, but can
be used by clients as one-time proxies.

@@

\section{Architecture}
% 3 pages

Dark Decoys involve three main steps. First, clients \textbf{register} with the
ISP station,
and agree on the dark decoy IP address that will be used. Next, the client
connects to the agreed upon address, which is terminated by an
\textbf{application} running on the station. Finally, the client \textbf{proves}
to the application that it was the same entity that registered (and not a censor
attempting to probe), and is able to use the application as a proxy.

Similar to previous schemes, our design does not require expensive in-line
flow blocking, and can be accomplished with only a passive tap at the ISP.
Our architecture is also modular, in that the registration and application steps operate
independently, allowing a wide range of flexibility to evade censors. We
describe each of these components.

\subsection{Registration}

Clients can register intent to use the proxy in several covert ways. For
instance, they could use email or other existing intermitently available proxies
to register. In this section, we use a form of Refraction Networking similar to
TapDance to register directly with the station.

Registration is unidirectional (client to server) and does not require any
acknowledgement of receipt. To ensure receipt, clients can attempt to register
multiple times (possibly via multiple methods) with the same information, and expect
that one gets through.

\medskip

To register, clients connect to a \textbf{decoy} site that supports TLS. They
complete the handshake, and send a normal HTTPS request. In TLS, requests (and
responses) are encrypted and sent in an \texttt{Application Data} record. During
registration, the client alters the ciphertext of the \texttt{Application Data} record to
convey a short \textbf{tag} to the ISP station, on path between the client and
decoy site.

The tag contains a public key (encoded to be indistinguishable from random using
Elligator~\cite{elligator}), and a message encrypted under the shared secret
derived from a key exchange with the station's long-term public key hard-coded
in the client software. The station uses its private key to compute the same
shared secret from the (decoded) public key, and decrypts the message in the
tag. The censor, without knowledge of either the station or client's private
key, cannot derive the shared secret, preventing it from being able to decrypt
the message.

Inside the message, the client communicates a random \textbf{seed}, and other
configuration-specific information, such as flags to signify version, feature
support, and which set of dark decoy network prefixes the client knows of. The
client and server use a hash of the provided seed to determine which specific
dark decoy IP address to register. It may seem intuitive to instead have the client
send the specific IP address to register, but allowing the client arbitrary
choice also allows censors to register suspected dark decoys and block them if
they pick up. By using a hash, the censor would have to pre-image the hash to
obtain a seed it could use to register for a desired IP address. It also gives a
secret (the seed) that only the client and station know, even after the client
connects to the dark decoy address.

% Note on IPv6 space? /32 of IPv6 is 96-bits to select...
We note that IP addresses are selected from unused but still routed address
space that passes by the ISP. Traffic to unrouted addresses would produce ICMP
responses that a censor could observe, and are also easily blocked with knowledge
of a routing table. Because we support the use of IPv6 addresses, censors will
also be unable to scan ahead of time to determine if the host has been there
previously, or what was there before. While they can probe suspected dark decoy
addresses after clients connect to them, at that point the address has already been
registered, preventing the censor from identifying differences in behavior
before and after registration.

Once the dark decoy IP address has been selected, the station watches for
packets destined to that address, and forwards them onto the dark decoy
\textbf{application}. The station can also optionally ignore packets not from
the source IP address of the registering client, so that to a probing censor,
the dark decoy appears to be firewalled off from all but the client.

@@

Once the client has registered, packets sent to the dark decoy IP address are
passed to the \textbf{application} running on the station. The application has
two main jobs: first, it must look like an innocuous legitimate service to the
censor, and second must allow the client to use it as a proxy.

Any protocol that satisfies these criteria can be used as an application. For
instance, \texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
Tor~\cite{tor} that could be
modified to meet these needs: it requires each endpoint to have knowledge of a
shared secret (which we can derive from the seed shared by the client and
station during registration), and attempts to be a protocol with no discernible
fingerprint. Probing censors that do not have the shared secret receive no
response, while clients that have the secret can communicate with the proxy.

However, even though \texttt{obfs4} is indistinguishable from random, there are
still known attacks that can differentiate it from other
traffic~\cite{wang2015seeing}. While we have yet to see evidence of such attacks
employed in practice by censors, we consider two alternatives built on TLS.

\subsubsection{Mask Sites}

TLS is a natural protocol for dark decoy applications, because it is ubiquitous on
the Internet (making it difficult for censors to block), while also providing
strong cryptographic protection against passive and active network adversaries.
However, there are several challenges to make it robust against censors that
wish to block a particular service.

This is because TLS sends important server-identifying content in plaintext
during the TLS handshake. This includes the Server Name Indication (SNI) in the
Client Hello message that sends the domain name of the server, and the
X.509 Certificate sent by the server.

To evade censors, we must send a plausible SNI value (sending no SNI is
uncommon and easily blocked---only 1\% of TLS connections do not carry the
SNI extension~\cite{tls-fingerprint}), and we must have the server respond with
a plausible (and corresponding) certificate. Even if we manage to avoid sending
either in the clear, censors could actively probe the server in a
way that would normally elicit a certificate.

We therefore attempt to mimic an existing \textbf{mask site}, by relaying
traffic between the client and a selected mask website. To a censor, this site
will be indistinguishable from the legitimate mask site, making it difficult for
them to block without potentially blocking the actual site. TLS connections to the
application will terminate exactly as connections to the mask site would, with the
application acting as a transparent proxy between the client and mask site.
However, this leaves the application unable to introspect on the contents of the
TLS connection to the mask site, as it does not have the client-site shared
secrets, and it cannot overtly man-in-the-middle the connection before knowing
it is communicating with the legitimate client (and not the censor).

To accomplish this, the client changes the shared secret it derives with the
mask site to something that the application can also derive. The client's first
\texttt{Application Data} packet is thus encrypted under a different secret than
the client/mask site secret. Specifically, the client uses the \textbf{seed}
sent during registration to derive the pre-master secret for the connection.
This is hashed along with the client and server randoms of the current (mask
site) TLS connection to obtain the master secret that determines
encryption/decryption/authentication keys.

The application can determine if the client did this by trial decryption with
the master secret derived from the known \textbf{seed}. If it succeeds, the
client has proved knowledge of the \textbf{seed}, and the application can
respond as a proxy. If not, the application simply continues to forward data
between the client and the mask site. As the censor does not have knowledge of
the \textbf{seed} used in registration, it cannot coerce the application to
appear as anything besides the mask site.

\paragraph{Mask Site Selection}
How do we get the list of masked sites? Alexa list? passive observation?

\subsubsection{Encrypted SNI}

TLS~1.3....

%-Registration
%-Dark decoy selection (seed -> IP)
%-Connection to Dark Decoy Application (DD App)
%-IPv6 vs IPv4 dark decoys
